\documentclass{article}
\usepackage{amsmath,amssymb,amsthm,latexsym,paralist}

\theoremstyle{definition}
\newtheorem{problem}{Problem}
\newtheorem*{solution}{Solution}
\newtheorem*{resources}{Resources}

\newcommand{\name}[2]{\noindent\textbf{Name: #1}\hfill \textbf{UIN: #2}}
\newcommand{\honor}{\noindent On my honor, as an Aggie, I have neither
  given nor received any unauthorized aid on any portion of the
  academic work included in this assignment. Furthermore, I have
  disclosed all resources (people, books, web sites, etc.) that have
  been used to prepare this homework. \\[2ex]
 \textbf{Electronic signature:} \underline{ \textbf{(type your full name here)} } }
 
\newcommand{\checklist}{\noindent\textbf{Checklist:}
\begin{compactitem}[$\Box$] 
\item Did you type in your name and UIN? 
\item Did you disclose all resources that you have used? \\
(This includes all people, books, websites, etc.\ that you have consulted.)
\item Did you sign that you followed the Aggie Honor Code? 
\item Did you solve all problems? 
\item Did you submit the .tex and .pdf files of your homework to the correct link on Canvas? 
\end{compactitem}
}

\newcommand{\problemset}[1]{\begin{center}\textbf{Problem Set #1}\end{center}}
\newcommand{\duedate}[1]{\begin{quote}\textbf{Due dates:} Electronic
    submission of \textsl{yourLastName-yourFirstName-hw3.tex} and 
    \textsl{yourLastName-yourFirstName-hw3.pdf} files of this homework is due on
    \textbf{#1} on \texttt{https://canvas.tamu.edu}. You will see two separate links
    to turn in the .tex file and the .pdf file separately. Please do not archive or compress the files.  
    \textbf{If any of the two files are missing or unreadable, you will receive zero points for this
    homework.}\end{quote} }

\newcommand{\N}{\mathbf{N}}
\newcommand{\R}{\mathbf{R}}
\newcommand{\Z}{\mathbf{Z}}


\begin{document}
\vspace*{-20mm}
\begin{center}
{\large
CSCE 222 Discrete Structures for Computing -- Fall 2021\\[.5ex]
Hyunyoung Lee\\}
\end{center}
\problemset{3}
\duedate{Friday, 9/24/2021 11:59 p.m.}
\name{ (type your name here) }{ (type your UIN here) }
\begin{resources} (All people, books, articles, web pages, etc.\ that
  have been consulted when producing your answers to this homework)
\end{resources}
\honor

\bigskip

\noindent
Total 100 points.

\bigskip

\noindent
The problems are from the lecture notes posted on Perusall.

\medskip

\begin{problem} (15 points) Section 2.9, Exercise 2.35 
\end{problem}
\begin{solution} 
\end{solution}

\begin{problem} (15 points) Section 2.9, Exercise 2.36
\end{problem}
\begin{solution} 
\end{solution}

\begin{problem} (20 points) Section 2.9, Exercise 2.41
\end{problem}
\begin{solution} 
\end{solution}

\begin{problem} (20 points) Section 2.9, Exercise 2.45
\end{problem}
\begin{solution} 
\end{solution}

\begin{problem} (5 points $\times$ 2 = 10 points) Section 3.1, Exercise 3.4 (a) and (c) 
\end{problem}
\begin{solution} 
\end{solution}

\begin{problem} (20 points) Section 3.1, Exercise 3.5 [Hint: Use the definition of $\subseteq$]
\end{problem}
\begin{solution} 
\end{solution}

\goodbreak
\checklist
\end{document}
